### 2015-01-09 paper/Content/01introduction.tex
updated introduction.

However, not having clear rules regarding the application's architecture entails risks, especially for people that are not expert-level developers. Applications become larger from time to time, and without a reasonable architecture this leads to complex code which is hard to understand and maintain \cite{PassiveMVC, BallOfMud}. Additionally, complex dependencies in the SDK cause messy code and make it hard to exchange specific elements without affecting other elements \cite{PassiveMVC}.\\ \todo[inline]{Testability einfügen -- Wie lässt sich das Problem zusammenfassen?}

>>>>

However, not having clear rules regarding the application's architecture entails risks, especially for people that are not expert-level developers. Applications become larger from time to time, and without a reasonable architecture this leads to complex code which is hard to understand and maintain \cite{PassiveMVC, BallOfMud}. Additionally, complex dependencies in the SDK cause messy code and make it hard to exchange specific elements without affecting other elements \cite{PassiveMVC}. That is especially because \emph{Android} tends to lead to classes containing a lot of functionality, which often requires more effort concerning testability and extendability \cite{GangOfFour}. \\
